---
title: "Prac02"
author: "Pedro Albarran"
date: "19 de octubre de 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

*** De Rgraphics

Exercise I
----------

The data for the exercises is available in the `dataSets/EconomistData.csv` file. Read it in with

``` r
  dat <- read.csv("dataSets/EconomistData.csv")
```

Original sources for these data are <http://www.transparency.org/content/download/64476/1031428> <http://hdrstats.undp.org/en/indicators/display_cf_xls_indicator.cfm?indicator_id=103106&lang=en>

These data consist of *Human Development Index* and *Corruption Perception Index* scores for several countries.

1.  Create a scatter plot with CPI on the x axis and HDI on the y axis.
2.  Color the points in the previous plot blue.
3.  Color the points in the previous plot according to *Region*.
4.  Create boxplots of CPI by Region
5.  Overlay points on top of the box plots

Exercise I prototype<span class="tag" data-tag-name="prototype"></span>
-----------------------------------------------------------------------

1.  \[@1\] Create a scatter plot with CPI on the x axis and HDI on the y axis.

``` r
  ggplot(dat, aes(x = CPI, y = HDI)) +
    geom_point()
```

1.  \[@2\] Color the points in the previous plot blue.

``` r
  ggplot(dat, aes(x = CPI, y = HDI)) +
    geom_point(color = "blue")
```

1.  \[@3\] Color the points in the previous plot according to *Region*.

``` r
  ggplot(dat, aes(x = CPI, y = HDI)) +
    geom_point(aes(color = Region))
```

1.  \[@4\] Create boxplots of CPI by Region

``` r
  ggplot(dat, aes(x = Region, y = CPI)) +
    geom_boxplot()
```

1.  \[@5\] Overlay points on top of the box plots

``` r
  ggplot(dat, aes(x = Region, y = CPI)) +
    geom_boxplot() +
    geom_point() 
```



Exercise II
-----------

1.  Re-create a scatter plot with CPI on the x axis and HDI on the y axis (as you did in the previous exercise).
2.  Overlay a smoothing line on top of the scatter plot using the *lm* method. Hint: see `?stat_smooth`.
3.  Overlay a smoothing line on top of the scatter plot using the default method.
4.  BONUS (optional): Overlay a smoothing line on top of the scatter plot using the default *loess* method, but make it less smooth. Hint: see `?loess`.

Exercise II prototype<span class="tag" data-tag-name="prototype"></span>
------------------------------------------------------------------------

1.  \[@1\] Re-create a scatter plot with CPI on the x axis and HDI on the y axis (as you did in the previous exercise).

```{r, echo=T, eval=F}
  ggplot(dat, aes(x = CPI, y = HDI)) +
    geom_point()
```

1.  \[@2\] Overlay a smoothing line on top of the scatter plot using the *lm* method. Hint: see `?stat_smooth`.

```{r, echo=T, eval=F}
  ggplot(dat, aes(x = CPI, y = HDI)) +
    geom_point() +
    geom_smooth(method = "lm")
```

1.  \[@3\] Overlay a smoothing line on top of the scatter plot using the default method.

```{r, echo=T, eval=F}
  ggplot(dat, aes(x = CPI, y = HDI)) +
    geom_point() +
    geom_smooth()
```

1.  \[@4\] BONUS (optional): Overlay a smoothing line on top of the scatter plot using the default *loess* method, but make it less smooth. Hint: see `?loess`.

```{r, echo=T, eval=F}
  ggplot(dat, aes(x = CPI, y = HDI)) +
    geom_point() +
    geom_smooth(span = .4)
```


Exercise III
------------

1.  Create a scatter plot with CPI on the x axis and HDI on the y axis. Color the points to indicate region.
2.  Modify the x, y, and color scales so that they have more easily-understood names (e.g., spell out "Human development Index" instead of "HDI").
3.  Modify the color scale to use specific values of your choosing. Hint: see `?scale_color_manual`.

Exercise III prototype<span class="tag" data-tag-name="prototype"></span>
-------------------------------------------------------------------------

1.  \[@1\] Create a scatter plot with CPI on the x axis and HDI on the y axis. Color the points to indicate region.

```{r, echo=T, eval=F}
  ggplot(dat, aes(x = CPI, y = HDI, color = "Region")) +
    geom_point()
```

1.  \[@2\] Modify the x, y, and color scales so that they have more easily-understood names (e.g., spell out "Human development Index" instead of "HDI").

```{r, echo=T, eval=F}
  ggplot(dat, aes(x = CPI, y = HDI, color = "Region")) +
  geom_point() +
  scale_x_continuous(name = "Corruption Perception Index") +
  scale_y_continuous(name = "Human Development Index") +
  scale_color_discrete(name = "Region of the world")
```

1.  \[@3\] Modify the color scale to use specific values of your choosing. Hint: see `?scale_color_manual`.

```{r, echo=T, eval=F}
  ggplot(dat, aes(x = CPI, y = HDI, color = "Region")) +
  geom_point() +
  scale_x_continuous(name = "Corruption Perception Index") +
  scale_y_continuous(name = "Human Development Index") +
    scale_color_manual(name = "Region of the world",
                       values = c("#24576D",
                                  "#099DD7",
                                  "#28AADC",
                                  "#248E84",
                                  "#F2583F",
                                  "#96503F"))
```


ejercicio de la NASA de https://beanumber.github.io/sds192/lab-colorbrewer-ggthemes.html
